Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-12 hotstorage13/eval.tex
w

We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.

Objectives of our evaluation are:
1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.
2) Examine the impacts of buffering during metadata exchange.

@@

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE} and each
of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks ~\cite{similar94} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O bandwidth of local storage is about 50MB/second 
in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
over 300MB/second with 4 drives or more and our setting uses
16.7\% or less of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster. 
%and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
%  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second

>>>>

We have implemented and evaluated a prototype of our multi-stage deduplication scheme on a Linux cluster
of multi-core AMD Bulldozer FX8120 and Intel Nehalem E5530 machines.  
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Objectives of our evaluation are:
1) Analyze the deduplication throughput and effectiveness for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.
2) Examine the impacts of buffering during metadata exchange.

@@

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE} and each
of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O bandwidth of local storage is about 50MB/second 
in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
over 300MB/second with 4 drives or more and our setting uses
16.7\% or less of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster. 
%and that translates to an aggregated backup throughput of 139GB per second, or 500TB per hour.
%  For 2 hours, every machine can do 139MB/second. For 3 hours, then 92MB/second
